Visualization tool for comparison of a single amino acid change in protein simulation

### 2017-06-29 paper/paper.tex
paper figs
paper

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Visualization tool for comparison of amino acids in protein simulations}

@@

%------------------------------------------------------------------------- 
% Special Sibgrapi teaser
\teaser{%
  \oneimage{Teasing result of our method: from this data input (left), the relevant feature are extracted using our technique (middle), producing effective result (right).}{.99}{sibgrapi.png}
}
%-------------------------------------------------------------------------

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Visualization tool for comparison of a single amino acid change in protein simulation}

@@

%------------------------------------------------------------------------- 
% Special Sibgrapi teaser
\teaser{%
  \oneimage{Image of the tool with all elements presented.}{.99}{all.png}
}
%-------------------------------------------------------------------------
